Verifying Demonstrations

### 2018-05-23 paper/analysis-security.tex
Makes proper multiletter variables

\subsection{Constructing the participation-proof shares}

\subsubsection{Linkability and designated protest}

\NewVariable{\sk}{sk}

\Cref{CountOnce} is required to prevent Sybil attacks, \ie that one individual 
can provide two participation proofs and thus be counted twice.
This is prevented by the use of \(\pid\).
To be counted twice, Alice must produce a \(\pid'\neq \pid\) and a signature
\begin{align*}
\pi_{\pid'} &= \SPK\mleft\{ (\sk') : \mright. \\
            & \qquad pid = \ACprf[_{\sk'}][cid], \\
            & \qquad \mleft. \sigma = \ACblind[\ACsign[_{ssk}][\sk']] \mright\} 
            \\
            & \qquad\qquad (\cid, \pid', \wid', t_s, t_s', l, wsig').
\end{align*}
\daniel{There are several approaches for Alice to do this, we should describe 
  them.}

@@

\subsubsection{Temporal eligibility, created after start}

@@

\subsubsection{Location proofs and spatial eligibility}

@@

Alice will send her \(pid\) to Jane to start the witness protocol.
Then they do the distance bounding \dots
[See issue \#22 for the discussion.]
If Jane is convinced that Alice's secret is within the desired proximity, she 
will compute her witness identifier \(wid\) and witness signature \(wsig\) and 
send them to Alice.

\subsubsection{Temporal eligibility, created before end}

@@

Universal verifiability (\cref{UniversalVerif}) means that anyone should be able 
to count the valid proofs.
To do this we must be able to verify the eligibility of a proof (\ie of all 
its shares) and then count it if valid.
To verify the eligibility of a proof share, we must verify that \(pid\), \(wid\) 
and \(wsig\) are not just randomly generated numbers but they actually depend on 
the keys \(k_P\) and \(k_W\) (as illustrated in \cref{fig:ProofFig}).
We will do this with \ac{NIZK} proofs.
We note that these proofs are not needed until the verification step after the 
protest.
Thus \(pid, wid, wsig\) can be used in the proof shares (and all computations 
above) whereas their respective \ac{NIZK} proof can be computed and published 
after the protest.

Alice must provide \iac{NIZK} proof showing that \(pid = \ACprf[_{k_P}][cid]\) 
and that she knows a signature by the identity authority on \(k_P\).
\dots
[Details of how to do this, or maybe that will be in \cref{BuildingBlocks}. See 
issue \#27 for discussion.]

In the same manner, each witness must also provide \iac{NIZK} proofs for \(wid = 
  \ACprf[_{k_W}][pid]\) and \(wsig = \ACprf[_{k_W}][wid, t_s, l]\) as well as 
that the witness knows a signature by the identity authority on \(k_W\).
With these \ac{NIZK} proofs anyone can verify the validity, \ie the 
eligibility, of the proof shares and thus also count them.

@@

More specifically, to achieve receipt freeness (\cref{ReceiptFreeness}) Alice 
must remove her secret \ac{PRF} key, \(k_A\).
With this key Grace can verify that Alice has submitted a proof by computing 
\(pid'\gets \ACprf[_{k_A}][cid]\) and compare \(pid = pid'\).

>>>>

\paragraph{Linkability and designated protest}

\Cref{CountOnce} is required to prevent Sybil attacks, \ie that one individual 
can provide two participation proofs and thus be counted twice.
This is prevented by the use of \(\pid\).
To be counted twice, Alice must produce a \(\pid'\neq \pid\) and a signature
\begin{multline*}
\pi_{\pid'} = \SPK\mleft\{ (\sk') : \mright. \\
  \begin{aligned}
    \pid' &= \ACprf[_{\sk'}][\cid], \\
    \sigma &= \mleft. \ACblind[\ACsign[_{\ssk}][\sk']] \mright\}
  \end{aligned} \\
    (\cid, \pid', \wid', t_s, t_s', l, \wsig').
\end{multline*}
\daniel{There are several approaches for Alice to do this, \eg attacking the 
  \(\SPK\)-signature, the \(\AC\)-signature, \etc.
  I think we should describe them.}

@@

\paragraph{Temporal eligibility, created after start}

@@

\paragraph{Location proofs and spatial eligibility}

@@

Alice will send her \(\pid\) to Jane to start the witness protocol.
Then they do the distance bounding \dots
[See issue \#22 for the discussion.]
If Jane is convinced that Alice's secret is within the desired proximity, she 
will compute her witness identifier \(\wid\) and witness signature \(\wsig\) and 
send them to Alice.

\paragraph{Temporal eligibility, created before end}

@@

Universal verifiability (\cref{UniversalVerif}) means that anyone should be able 
to count the valid proofs.
To do this we must be able to verify the eligibility of a proof (\ie of all 
its shares) and then count it if valid.
To verify the eligibility of a proof share, we must verify that \(\pid\), \(\wid\) 
and \(\wsig\) are not just randomly generated numbers but they actually depend on 
the keys \(k_P\) and \(k_W\) (as illustrated in \cref{fig:ProofFig}).
We will do this with \ac{NIZK} proofs.
We note that these proofs are not needed until the verification step after the 
protest.
Thus \(\pid, \wid, \wsig\) can be used in the proof shares (and all computations 
above) whereas their respective \ac{NIZK} proof can be computed and published 
after the protest.

Alice must provide \iac{NIZK} proof showing that \(\pid = \ACprf[_{k_P}][\cid]\) 
and that she knows a signature by the identity authority on \(k_P\).
\dots
[Details of how to do this, or maybe that will be in \cref{BuildingBlocks}. See 
issue \#27 for discussion.]

In the same manner, each witness must also provide \iac{NIZK} proofs for \(\wid = 
  \ACprf[_{k_W}][\pid]\) and \(\wsig = \ACprf[_{k_W}][\wid, t_s, l]\) as well as 
that the witness knows a signature by the identity authority on \(k_W\).
With these \ac{NIZK} proofs anyone can verify the validity, \ie the 
eligibility, of the proof shares and thus also count them.

@@

More specifically, to achieve receipt freeness (\cref{ReceiptFreeness}) Alice 
must remove her secret \ac{PRF} key, \(k_A\).
With this key Grace can verify that Alice has submitted a proof by computing 
\(\pid'\gets \ACprf[_{k_A}][\cid]\) and compare \(\pid = \pid'\).

### 2018-05-23 paper/protocol.tex
Makes proper multiletter variables

\NewAlgorithm{\PRIVOsetup}{Setup}

\emph{Setup: \((spk, ssk)\gets \PRIVOsetup\).}
The setup phase is for the \ac{CA} to set up all the needed keys.
The \ac{CA} generates a service public-private key-pair \((spk, ssk)\) as 
follows.
Let \(G = \gen g\) be a group with generator \(g\) and prime order \(q\).
Let \(G_T\) be a group such that there is a bilinear pairing \(e\colon G\times 
  G\to G_T\)\footnote{%
  \Ie \(e(g_1^a, g_2^b) = e(g_1, g_2)^{ab}\) and if \(G = \gen{g_1} = 
    \gen{g_2}\) then \(G_T = \gen{e(g_1, g_2)}\).
}.
Choose \(x,y,z\rgets \ZZ_q\) uniformly at random and set \(X = g^x, Y = g^y, Z = 
  g^z\).
Then the service public key \(spk = (q, G, G_T, g, X, Y, Z)\) and the service 
private key \(ssk = (x, y, z)\).

@@

\emph{Registration: \(sk\gets 
    \Proto{\PRIVOreg[_P][spk]}{\PRIVOreg[_{CA}][ssk]}\).}
During the registration phase, each protester will generate a secret key and 
obtain a signature on it by the \ac{CA} --- without revealing it to the \ac{CA}.
Thus each protester will have a signed secret key, the \ac{CA} will issue only 
one signature per protester but will not know who has which key.
The protester chooses \(k, r\rgets \ZZ_q\) uniformly randomly and sets \(M = g^k 
  Z^r\) and sends \(M\) to the server.
The protester acts as prover and the \ac{CA} as verifier while they perform the 
following \ac{ZKPK} protocol:
\[
  \PK[k,r][M = g^k Z^r].
\]
If the proof succeeds, the \ac{CA} chooses \(a\rgets \ZZ_q^*\) and sets \(A = 
  g^a\).
Then it forms the signature \(\sigma = (A, B = A^y, Z_B = B^z = Z^{ay}, C = A^x 
  M^{axy})\) and sends it to the protester.
The protester verifies that the following equations hold:
\begin{align*}
  A &\neq 1 \\
  e(g, B) &= e(Y, A) \\
  e(g, Z_B) &= e(Z, B) \\
  e(g, C) &= e(X, A) e(X, B)^k e(X, Z_B)^r.
\end{align*}
Upon success, the protester uses \(sk = (\sigma, k, r)\).

@@

\NewAlgorithm{\PRIVOjoin}{Join}
\NewVariable{\mfst}{manifesto}

\emph{Joining participant: \((pid, t_s)\gets 
    \PRIVOjoin[_P][\text{manifesto}]\).}
A participant who wants to join the protest will use the manifesto to compute an 
identifier for the cause, \(cid\gets \Hash[\mfst]\).
Then this identifier is used to create the participant's protest-specific 
identifier, \(pid\gets \ACprf[_{sk}][cid]\) (in 
\cref{fig:ProofFig,fig:ProtocolOverview}).
More specifically, \(pid = g_T^{1/(k+cid)}\) (remember that \(sk = (\sigma, k, 
  r)\)).
The participant should also get a time-correlated random value from the 
time-stamping service, \(t_s\gets \TSget\).

\begin{figure}
  \centering
  \footnotesize
  \includegraphics{proofshare.tikz}
  \caption{%
    Structure of a proof share.
    The protester \(P\)'s identifier \(pid\) is computed using the protester's 
    key \(k_P\).
    The witness \(W\)'s identifier \(wid\) is computed using the witness's key 
    \(k_W\).
    \(t_s\) is a time interval and \(l\) is the coordinates of an area.
    The protest (cause) identifier \(cid\) is the hash value of the manifesto.
  }%
  \label{fig:ProofFig}
\end{figure}%

\begin{figure}
  \centering
  \footnotesize
  \begin{minipage}{\linewidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & t_s\gets \TSget \\
        & cid\gets \Hash[\text{manifesto}], \\
        & pid\gets \ACprf[_{sk_P}][cid] \\
      W\colon & t_s'\gets \TSget
      \\[-1em]
      \noalign{\hfill Join}
      \midrule
      \noalign{\hfill Participation}
      \\[-3em]
      P\to W\colon & pid \\
      P\leftrightarrow W\colon &
        \DBPK\mleft\{ (sk_P) : \mright. \\
        & \qquad pid = \ACprf[_{sk_P}][cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{ssk}][sk_P]] \mright\} 
        \\
      W\colon & wid\gets \ACprf[_{sk_W}][pid], \\
        & wsig\gets \ACprf[_{sk_W}][wid, t_s, t_s', l] \\
      W\to P\colon & (wid, t_s', l, wsig)
      \\[-1em]
      \noalign{\hfill Participation}
      \midrule
      \noalign{\hfill Submission}
      \\[-2em]
      P\colon & t_e\gets \TSstamp[\Hash[pid, wid, t_s, t_s', l, wsig]] \\
      W\colon & t_e'\gets \TSstamp[\Hash[pid, wid, t_s, t_s', l, wsig]] \\
      W\to S\colon & (pid, wid, t_s, t_s', t_e, l, wsig, \pi_{wid, wsig}),\quad 
      \text{where} \\
        & \pi_{wid, wsig} = \SPK\mleft\{ (sk_W) : \mright. \\
        & \qquad wid = \ACprf[_{sk_W}][pid], \\
        & \qquad wsig = \ACprf[_{sk_W}][wid, t_s, t_s', l], \\
        & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{ssk}][sk_W]]\mright\} \\
        & \qquad\qquad (pid, wid, t_s, t_s', l, wsig) \\
      P\to S\colon & (cid, pid, wid, t_s, t_s', t_e, l, wsig, \pi_{pid}),\quad 
      \text{where}\\
        & \pi_{pid} = \SPK\mleft\{ (sk_P) : \mright. \\
        & \qquad pid = \ACprf[_{sk_P}][cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{ssk}][sk_P]] \mright\} 
        \\
        & \qquad\qquad (cid, pid, wid, t_s, t_s', l, wsig)
    \end{align*}
  \end{minipage}
  \caption{%
    An overview of of the Join, Participation and Submission phases of \PRIVO.\@
    The organizer \(O\) broadcasts the manifesto.
    The protester \(P\), witness \(W\) and their computations are as in 
    \cref{fig:ProofFig}.
    Finally, both \(P\) and \(W\) submits the proof share to some permanent 
    storage \(S\).
  }%
  \label{fig:ProtocolOverview}
\end{figure}

@@

\emph{Participating: \(\pi\gets
    \Proto{\PRIVOparticipate[cid, sk_P]}{\PRIVOwitness[sk_W, spk]}\),}
In the participating phase the participant and the witness constructs the proof 
share of the participant (\cref{fig:ProofFig}).
The participant reblinds its signature \(\sigma\) on its secret key: choose 
\(r_1, r_2\rgets \ZZ_q^*\) and let \(
  \tilde\sigma = (\tilde A = A^{r_1},
                  \tilde B = B^{r_1},
                  \tilde Z_B = Z_B^{r_1},
                  \hat C = C^{r_1 r_2}).
\) (It is not necessary to compute a new \(\tilde\sigma\) more than once per 
\(pid\).)
The participant sends \((pid, \tilde\sigma)\) to the witness.
The witness verifies that
\begin{align*}
  \tilde A          &\neq 1 \\
  e(g, \tilde B)    &= e(Y, \tilde A) \\
  e(g, \tilde Z_B)  &= e(Z, \tilde B).
\end{align*}
Both the participant and the witness compute
\begin{align*}
  v &= e(g, \hat C) \\
  v_x &= e(X, \tilde A) \\
  v_{xy} &= e(X, \tilde B) \\
  v_{xy}' &= e(X, \tilde Z_B).
\end{align*}
Then they run the following \ac{DBPK} with the participant as the prover and the 
witness as the verifier:
\begin{multline*}
  \mleftright
  \DBPK\left\{(k, r, r') : v^{r'} = v_x v_{xy}^k v_{xy}^{\prime r} \land
    pid = g_T^{1/(k+cid)} \right\}.
\end{multline*}
where \(r' = 1/r_2\).
We can rewrite \(pid = g_T^{1/(k+cid)}\) as \(pid^k = g_T g_T^{-cid}\).
Then the \ac{PK} can be designed as follows (remember that this \ac{PK} should 
be run as \iac{DBPK} and be repeated multiple times to achieve security).
The participant chooses \(r_k, r_r, r_{r'}\rgets \ZZ_q\) uniformly randomly, 
sets \(R_1 = v^{r_{r'}} v_{xy}^{r_k} v_{xy}^{\prime r_r}\) and \(R_2 = 
  pid^{r_k}\) and sends \(R_1, R_2\) to the witness.
The witness replies with a challenge \(c\).
The participant then computes
\begin{align*}
s_k &= -ck + r_k, \\
s_r &= -cr + r_r, \\
s_{r'} &= cr' + r_{r'}
\end{align*}
and sends them to the witness.
The witness checks whether
\begin{align*}
  v_x^c R_1 &\overset{\mathclap{?}}{=} v^{s_{r'}} v_{xy}^{s_k} v_{xy}^{\prime 
    s_r}, \\
  \mleft(g_T pid^{-cid}\mright)^{-c} R_2 &\overset{\mathclap{?}}{=} pid^{s_k}.
\end{align*}
If the proof succeeds the witness will compute \(wid\gets \ACprf[_{sk_W}][pid] = 
  g_T^{1/(k_W+pid)}\) (as above) and in the same way \(wsig\gets 
  \ACprf[_{sk_W}][\Hash[pid, wid, t_s, t_s', l]]\).
Then the witness returns \((wid, t_s', l, wsig)\) to the participant.
Now both the participant and the witness have the tuple \(\pi = (pid, wid, t_s, 
  t_s', l, wsig)\) which constitutes a proof share of the participant 
(\cref{fig:ProofFig}).

@@

\emph{Submission: \(\pi'\gets \PRIVOsubmit[_P][cid, pid, wid, t_s, t_s', l, 
    wsig]\).}
The participant should as soon as possible commit the proof-share data to the 
time-stamping service and receive the proof of commitment, \(t_e\gets 
  \TSstamp[\Hash[pid, wid, t_s, t_s', l, wsig]]\).
The remaining operations are not time critical.
The participant computes \iac{NIZK} proof \(\pi_{pid}\) which shows the 
correctness of \(pid\).
More specifically,
\begin{multline*}
  \pi_{pid}\gets \SPK\left\{ (sk_P) : \right. \\
    \begin{aligned}
      pid &= \ACprf[_{sk_P}][cid] \quad \land \\
      \sigma_P' &= \left. \ACblind[\ACsign[_{ssk}][sk_P]] \right\}
    \end{aligned} \\
      (cid, pid, wid, t_s, t_s', l, wsig).
\end{multline*}
Finally, the participant uploads the tuple \[
  (cid, pid, wid, t_s, t_s', t_e, l, wsig, \pi_{pid})
\] for permanent storage.

\emph{Submission: \(\pi''\gets \PRIVOsubmit[_W][pid, wid, t_s, t_s', l, 
    wsig]\).}
The witness should, just as the participant, commit the proof-share data to the 
time-stamping service, \(t_e'\gets \TSstamp[\Hash[pid, wid, t_s, t_s', l, 
  wsig]]\).
(This is for redundancy only.)
Then, without any time requirements, the witness computes \iac{NIZK} proof 
\(\pi_{wid, wsig}\) as follows:
\begin{multline*}
  \pi_{wid, wsig}\gets \SPK\left\{ (sk_W) : \right. \\
    \begin{aligned}
      wid &= \ACprf[_{sk_W}][pid] \quad \land \\
      wsig &= \ACprf[_{sk_W}][wid, t_s, t_s', l] \quad \land \\
      \sigma_W' &= \left. \ACblind[\ACsign[_{ssk}][sk_W]] \right\}
    \end{aligned} \\
      (pid, wid, t_s, t_s', l, wsig).
\end{multline*}
Finally, the witness uploads the tuple \[
  (pid, wid, t_s, t_s', t_e', l, wsig, \pi_{wid, wsig})
\] for permanent storage.

>>>>

\NewAlgorithm{\PRIVOsetup}{Setup}
\NewVariable{\sk}{sk}
\NewVariable{\spk}{spk}
\NewVariable{\ssk}{ssk}

\emph{Setup: \((\spk, \ssk)\gets \PRIVOsetup\).}
The setup phase is for the \ac{CA} to set up all the needed keys.
The \ac{CA} generates a service public-private key-pair \((\spk, \ssk)\) as 
follows.
Let \(G = \gen g\) be a group with generator \(g\) and prime order \(q\).
Let \(G_T\) be a group such that there is a bilinear pairing \(e\colon G\times 
  G\to G_T\)\footnote{%
  \Ie \(e(g_1^a, g_2^b) = e(g_1, g_2)^{ab}\) and if \(G = \gen{g_1} = 
    \gen{g_2}\) then \(G_T = \gen{e(g_1, g_2)}\).
}.
Choose \(x,y,z\rgets \ZZ_q\) uniformly at random and set \(X = g^x, Y = g^y, Z = 
  g^z\).
Then the service public key \(\spk = (q, G, G_T, g, X, Y, Z)\) and the service 
private key \(\ssk = (x, y, z)\).

@@

\emph{Registration: \(\sk\gets 
    \Proto{\PRIVOreg[_P][\spk]}{\PRIVOreg[_{CA}][\ssk]}\).}
During the registration phase, each protester will generate a secret key and 
obtain a signature on it by the \ac{CA} --- without revealing it to the \ac{CA}.
Thus each protester will have a signed secret key, the \ac{CA} will issue only 
one signature per protester but will not know who has which key.
The protester chooses \(k, r\rgets \ZZ_q\) uniformly randomly and sets \(M = g^k 
  Z^r\) and sends \(M\) to the server.
The protester acts as prover and the \ac{CA} as verifier while they perform the 
following \ac{ZKPK} protocol:
\[
  \PK[k,r][M = g^k Z^r].
\]
If the proof succeeds, the \ac{CA} chooses \(a\rgets \ZZ_q^*\) and sets \(A = 
  g^a\).
Then it forms the signature \(\sigma = (A, B = A^y, Z_B = B^z = Z^{ay}, C = A^x 
  M^{axy})\) and sends it to the protester.
The protester verifies that the following equations hold:
\begin{align*}
  A &\neq 1 \\
  e(g, B) &= e(Y, A) \\
  e(g, Z_B) &= e(Z, B) \\
  e(g, C) &= e(X, A) e(X, B)^k e(X, Z_B)^r.
\end{align*}
Upon success, the protester uses \(\sk = (\sigma, k, r)\).

@@

\NewAlgorithm{\PRIVOjoin}{Join}
\NewVariable{\mfst}{manifesto}
\NewVariable{\cid}{cid}
\NewVariable{\pid}{pid}

\emph{Joining participant: \((\pid, t_s)\gets 
    \PRIVOjoin[_P][\text{manifesto}]\).}
A participant who wants to join the protest will use the manifesto to compute an 
identifier for the cause, \(\cid\gets \Hash[\mfst]\).
Then this identifier is used to create the participant's protest-specific 
identifier, \(\pid\gets \ACprf[_{\sk}][\cid]\) (in 
\cref{fig:ProofFig,fig:ProtocolOverview}).
More specifically, \(\pid = g_T^{1/(k+\cid)}\) (remember that \(\sk = (\sigma, 
  k, r)\)).
The participant should also get a time-correlated random value from the 
time-stamping service, \(t_s\gets \TSget\).

\NewVariable{\wid}{wid}
\NewVariable{\wsig}{wsig}

\begin{figure}
  \centering
  \footnotesize
  \includegraphics{proofshare.tikz}
  \caption{%
    Structure of a proof share.
    The protester \(P\)'s identifier \(\pid\) is computed using the protester's 
    key \(k_P\).
    The witness \(W\)'s identifier \(\wid\) is computed using the witness's key 
    \(k_W\).
    \(t_s\) is a time interval and \(l\) is the coordinates of an area.
    The protest (cause) identifier \(\cid\) is the hash value of the manifesto.
  }%
  \label{fig:ProofFig}
\end{figure}%

\begin{figure}
  \centering
  \footnotesize
  \begin{minipage}{\linewidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & t_s\gets \TSget \\
        & \cid\gets \Hash[\text{manifesto}], \\
        & \pid\gets \ACprf[_{\sk_P}][\cid] \\
      W\colon & t_s'\gets \TSget
      \\[-1em]
      \noalign{\hfill Join}
      \midrule
      \noalign{\hfill Participation}
      \\[-3em]
      P\to W\colon & \pid \\
      P\leftrightarrow W\colon &
        \DBPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
      W\colon & \wid\gets \ACprf[_{\sk_W}][\pid], \\
        & \wsig\gets \ACprf[_{\sk_W}][\wid, t_s, t_s', l] \\
      W\to P\colon & (\wid, t_s', l, \wsig)
      \\[-1em]
      \noalign{\hfill Participation}
      \midrule
      \noalign{\hfill Submission}
      \\[-2em]
      P\colon & t_e\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l, \wsig]] \\
      W\colon & t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l, \wsig]] \\
      W\to S\colon & (\pid, \wid, t_s, t_s', t_e, l, \wsig, \pi_{\wid, 
        \wsig}),\quad \text{where} \\
        & \pi_{\wid, \wsig} = \SPK\mleft\{ (\sk_W) : \mright. \\
        & \qquad \wid = \ACprf[_{\sk_W}][\pid], \\
        & \qquad \wsig = \ACprf[_{\sk_W}][\wid, t_s, t_s', l], \\
        & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{\ssk}][\sk_W]]\mright\} 
        \\
        & \qquad\qquad (\pid, \wid, t_s, t_s', l, \wsig) \\
      P\to S\colon & (\cid, \pid, \wid, t_s, t_s', t_e, l, \wsig, 
      \pi_{\pid}),\quad \text{where}\\
        & \pi_{\pid} = \SPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l, \wsig)
    \end{align*}
  \end{minipage}
  \caption{%
    An overview of of the Join, Participation and Submission phases of \PRIVO.\@
    The organizer \(O\) broadcasts the manifesto.
    The protester \(P\), witness \(W\) and their computations are as in 
    \cref{fig:ProofFig}.
    Finally, both \(P\) and \(W\) submits the proof share to some permanent 
    storage \(S\).
  }%
  \label{fig:ProtocolOverview}
\end{figure}

@@

\emph{Participating: \(\pi\gets
    \Proto{\PRIVOparticipate[\cid, \sk_P]}{\PRIVOwitness[\sk_W, \spk]}\),}
In the participating phase the participant and the witness constructs the proof 
share of the participant (\cref{fig:ProofFig}).
The participant reblinds its signature \(\sigma\) on its secret key: choose 
\(r_1, r_2\rgets \ZZ_q^*\) and let \(
  \tilde\sigma = (\tilde A = A^{r_1},
                  \tilde B = B^{r_1},
                  \tilde Z_B = Z_B^{r_1},
                  \hat C = C^{r_1 r_2}).
\) (It is not necessary to compute a new \(\tilde\sigma\) more than once per 
\(\pid\).)
The participant sends \((\pid, \tilde\sigma)\) to the witness.
The witness verifies that
\begin{align*}
  \tilde A          &\neq 1 \\
  e(g, \tilde B)    &= e(Y, \tilde A) \\
  e(g, \tilde Z_B)  &= e(Z, \tilde B).
\end{align*}
Both the participant and the witness compute
\begin{align*}
  v &= e(g, \hat C) \\
  v_x &= e(X, \tilde A) \\
  v_{xy} &= e(X, \tilde B) \\
  v_{xy}' &= e(X, \tilde Z_B).
\end{align*}
Then they run the following \ac{DBPK} with the participant as the prover and the 
witness as the verifier:
\begin{multline*}
  \mleftright
  \DBPK\left\{(k, r, r') : v^{r'} = v_x v_{xy}^k v_{xy}^{\prime r} \land
    \pid = g_T^{1/(k+\cid)} \right\}.
\end{multline*}
where \(r' = 1/r_2\).
We can rewrite \(\pid = g_T^{1/(k+\cid)}\) as \(\pid^k = g_T g_T^{-\cid}\).
Then the \ac{PK} can be designed as follows (remember that this \ac{PK} should 
be run as \iac{DBPK} and be repeated multiple times to achieve security).
The participant chooses \(r_k, r_r, r_{r'}\rgets \ZZ_q\) uniformly randomly, 
sets \(R_1 = v^{r_{r'}} v_{xy}^{r_k} v_{xy}^{\prime r_r}\) and \(R_2 = 
  \pid^{r_k}\) and sends \(R_1, R_2\) to the witness.
The witness replies with a challenge \(c\).
The participant then computes
\begin{align*}
s_k &= -ck + r_k, \\
s_r &= -cr + r_r, \\
s_{r'} &= cr' + r_{r'}
\end{align*}
and sends them to the witness.
The witness checks whether
\begin{align*}
  v_x^c R_1 &\overset{\mathclap{?}}{=} v^{s_{r'}} v_{xy}^{s_k} v_{xy}^{\prime 
    s_r}, \\
  \mleft(g_T \pid^{-\cid}\mright)^{-c} R_2 &\overset{\mathclap{?}}{=} 
  \pid^{s_k}.
\end{align*}
If the proof succeeds the witness will compute \(\wid\gets 
  \ACprf[_{\sk_W}][\pid] = g_T^{1/(k_W+\pid)}\) (as above) and in the same way 
\(\wsig\gets \ACprf[_{\sk_W}][\Hash[\pid, \wid, t_s, t_s', l]]\).
Then the witness returns \((\wid, t_s', l, \wsig)\) to the participant.
Now both the participant and the witness have the tuple \(\pi = (\pid, \wid, 
  t_s, t_s', l, \wsig)\) which constitutes a proof share of the participant 
(\cref{fig:ProofFig}).

@@

\emph{Submission: \(\pi'\gets \PRIVOsubmit[_P][\cid, \pid, \wid, t_s, t_s', l, 
    \wsig]\).}
The participant should as soon as possible commit the proof-share data to the 
time-stamping service and receive the proof of commitment, \(t_e\gets 
  \TSstamp[\Hash[\pid, \wid, t_s, t_s', l, \wsig]]\).
The remaining operations are not time critical.
The participant computes \iac{NIZK} proof \(\pi_{\pid}\) which shows the 
correctness of \(\pid\).
More specifically,
\begin{multline*}
  \pi_{\pid}\gets \SPK\left\{ (\sk_P) : \right. \\
    \begin{aligned}
      \pid &= \ACprf[_{\sk_P}][\cid] \quad \land \\
      \sigma_P' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_P]] \right\}
    \end{aligned} \\
      (\cid, \pid, \wid, t_s, t_s', l, \wsig).
\end{multline*}
Finally, the participant uploads the tuple \[
  (\cid, \pid, \wid, t_s, t_s', t_e, l, \wsig, \pi_{\pid})
\] for permanent storage.

\emph{Submission: \(\pi''\gets \PRIVOsubmit[_W][\pid, \wid, t_s, t_s', l, 
    \wsig]\).}
The witness should, just as the participant, commit the proof-share data to the 
time-stamping service, \(t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l, 
  \wsig]]\).
(This is for redundancy only.)
Then, without any time requirements, the witness computes \iac{NIZK} proof 
\(\pi_{\wid, \wsig}\) as follows:
\begin{multline*}
  \pi_{\wid, \wsig}\gets \SPK\left\{ (\sk_W) : \right. \\
    \begin{aligned}
      \wid &= \ACprf[_{\sk_W}][\pid] \quad \land \\
      \wsig &= \ACprf[_{\sk_W}][\wid, t_s, t_s', l] \quad \land \\
      \sigma_W' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W]] \right\}
    \end{aligned} \\
      (\pid, \wid, t_s, t_s', l, \wsig).
\end{multline*}
Finally, the witness uploads the tuple \[
  (\pid, \wid, t_s, t_s', t_e', l, \wsig, \pi_{\wid, \wsig})
\] for permanent storage.
